Dark matter halo shape in the Auriga simulations: radial dependence, time evolution and correlation with baryon disk properties

### 2019-07-14 Document/paper.tex
new path

\begin{figure*}
\begin{center}
\includegraphics[width=0.9\columnwidth]{./pics/Triaxial_Plane/Lvl_4_Triax_Plane_DM.png}
 \includegraphics[width=0.9\columnwidth]{./pics/Triaxial_Plane/Lvl_4_Triax_Plane_MHD.png}
\end{center}
\caption{Axial ratios for the 30 halos in the Level 3 DM simulations
  on the left and MHD simulations on the right.
   Each dot represents the shape characterization of each halo 
   Red circles represent measurements at the virial radius and the
   blue squares are measurements at 1/8 of the virial radius.   
   The crosses represent the mean values and standard deviation of
   each sample.
   Overall we can see three things. 
   First, in DM only simulations halos are rounder in the outskirts
   than in the inner part.
   Second, halos in MHD are rounder than its DM only counterparts.
   Third, halos in MHD simulations are slightly rounder in the inner
   part compared to the outskirts.}
  \label{fig:triaxiality_plane}
\end{figure*}

@@

\begin{figure}
\includegraphics[width=0.9\columnwidth]{delta_triaxialiy_distro.pdf}
\caption{Cumulative fraction of the changes in the triaxility betwen
  MHD and DM simulations at different radii. 
  At all radii at least $80\%$ of the halos became rounder in the MHD
  simulations. 
  However, the effect is more pronounced at smaller radii.}
\label{fig:delta_triaxial_cumulative}
\end{figure}

>>>>

\begin{figure*}
\begin{center}
\includegraphics[width=0.9\columnwidth]{Lvl_4_Triax_Plane_DM.png}
 \includegraphics[width=0.9\columnwidth]{Lvl_4_Triax_Plane_MHD.png}
\end{center}
\caption{Axial ratios for the 30 halos in the Level 3 DM simulations
  on the left and MHD simulations on the right.
   Each dot represents the shape characterization of each halo 
   Red circles represent measurements at the virial radius and the
   blue squares are measurements at 1/8 of the virial radius.   
   The crosses represent the mean values and standard deviation of
   each sample.
   Overall we can see three things. 
   First, in DM only simulations halos are rounder in the outskirts
   than in the inner part.
   Second, halos in MHD are rounder than its DM only counterparts.
   Third, halos in MHD simulations are slightly rounder in the inner
   part compared to the outskirts.}
  \label{fig:triaxiality_plane}
\end{figure*}

@@

\begin{figure}
\includegraphics[width=0.9\columnwidth]{delta_triaxiality_distro.pdf}
\caption{Cumulative fraction of the changes in the triaxility betwen
  MHD and DM simulations at different radii. 
  At all radii at least $80\%$ of the halos became rounder in the MHD
  simulations. 
  However, the effect is more pronounced at smaller radii.}
\label{fig:delta_triaxial_cumulative}
\end{figure}
